DeepSphere: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2019-03-06 scnn.tex
fix footnote number

\begin{figure}[t!]
    \centering
    \includegraphics[height=7em]{sphere_grid_equirectangular}
    \hfill
    \includegraphics[height=7em]{sphere_grid_cubedsphere}
    \hfill
    \includegraphics[height=7em]{half_graph_4}
    \caption[]{Some pixelizations of the sphere. Left: the equirectangular grid, using equiangular spacing in a standard spherical-polar coordinate system. Middle: an equiangular cubed-sphere grid, as described in \citep{ronchi1996cubed}. Right: graph built from a HEALPix pixelization of half the sphere ($N_{side} = 4$). By construction, each vertex has eight neighbors, except the highlighted ones which have only seven.\footnotemark[4] Left and middle figures are taken from \citep{boomsma2017spherical}.}
    \label{fig:sphere_grids}
    \label{fig:healpix_graph_4}
\end{figure}

>>>>

\begin{figure}[t!]
    \centering
    \includegraphics[height=7em]{sphere_grid_equirectangular}
    \hfill
    \includegraphics[height=7em]{sphere_grid_cubedsphere}
    \hfill
    \includegraphics[height=7em]{half_graph_4}
    \caption[]{Some pixelizations of the sphere. Left: the equirectangular grid, using equiangular spacing in a standard spherical-polar coordinate system. Middle: an equiangular cubed-sphere grid, as described in \citep{ronchi1996cubed}. Right: graph built from a HEALPix pixelization of half the sphere ($N_{side} = 4$). By construction, each vertex has eight neighbors, except the highlighted ones which have only seven.\footnotemark[5] Left and middle figures are taken from \citep{boomsma2017spherical}.}
    \label{fig:sphere_grids}
    \label{fig:healpix_graph_4}
\end{figure}
